Reading Notes

### 2020-07-14 reading-notes.tex
read Schwarz

\cite{Schwarz2013}
read this with the intention of understanding how the CG potentials were derived.

>>>>

\cite{Schwarz2013}
read this with the intention of understanding how the CG potentials were derived.
OK I don't know what Langevin dynamics are but I think it means modelling molecular systems with reduced degrees of freedom and accounting for omitted dof using random kicks to the system?? Mimics solvent or atmospheric effects.
CG model matches experimental phase behaviour. 
ooh really nice figure showing the different length scales (diffraction peaks) in p3ht
diffraction can't resolve molecular level interactions.
this paper describes p3ht nanostructure formation in solution
model: equilibrium bond lengths, angles, charges from DFT. Based on OPLSAA. model agrees with density crystal structure, heat of sublimation. CG FF determined using IBI.
Simulations appear really low density compared to what I'm used to seeing.
